Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks

### 2020-03-16 paper/eccv2020submission.tex
Adding small paragraph to the evaluation

We adopt the objective for the discriminator network as we modify it slightly by leaving out the random vector $z$.
\begin{equation}
\mathcal{L}_{cGAN} (G, D) = (\mathbb{E}[\log D (x,y)] + \mathbb{E}[\log D (x, G(x))])/2
\end{equation}
where $x$ is the input image and $y$ is the target image. In contrast to unconditional GANs, both the generator and the discriminator network have access to the input image. The objective is divided by 2 to slow down the training of the discriminator relative to the generator as suggested by [].

@@

All of the models were trained and evaluated on a single Nvidia GTX 980Ti GPU.\@

@@

>>>>

We adopt the objective for the discriminator network as we modify it slightly by leaving out the random vector $z$.
\begin{equation}
\mathcal{L}_{cGAN} (G, D) = (\mathbb{E}[\log D (x,y)] + \mathbb{E}[\log D (x, G(x))])/2
\end{equation}
where $x$ is the input image and $y$ is the target image. In contrast to unconditional GANs, both the generator and the discriminator network have access to the input image. The objective is divided by two to slow down the training of the discriminator relative to the generator as suggested by [].

@@

All of the models were trained and evaluated on a single Nvidia GTX 980Ti GPU.\@ The implementation of the models was done in the PyTorch python library for machine leaning.

@@

When it comes to the evaluation, we have two separate views of the results generated by the models.

On one hand, we are dealing with image data that is meant to be perceived by human observer. This implies that full accuracy is not essential and therefore we place the importance on the perceived qualities of the results. This makes sense as in our case a human is concerned with the general development of the simulation over time. Under those consideration have chose appropriate metrics to compare the predicted simulation frames with the real ones. In this aspect, the first of the metrics that we have chose is Peak Signal to Noise Ratio (PSNR). It is related top the mean secured error (MSE) and it's given by
\begin{equation}
PSNR = 10 \cdot \log_{10}\left(\frac{255^2}{MSE}\right)
\end{equation}
PSNR is measured in decibel (dB) and it is a common metric used to evaluate lossy compression algorithms. It measures the difference between original and reconstructed image and considers the fidelity of the reconstruction. This makes the metric suitable in our case. Typical PSNR values of lossy image and video compression  algorithms are between 30 and 50 dB.
